\thesistitle

### 2019-06-12 sections/research.tex
Various changes

\section{Unifying the types}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slighly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.

@@

\section{Suitability of existing Clone Detection Tools towards our refactoring purposes}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview.
\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored. Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}

None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}. This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.

@@

\subsection{Clone Detection}
To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. On basis of this graph structure, clones are detection. Dependent on the type of clones being detected, transformations may be applied. The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{section:clonephilosophy}.

>>>>

\section{Unifying the types}\label{sec:unifying}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slighly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.

@@

\section{Suitability of existing Clone Detection Tools for detecting these clones}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview. We analyzed this behavior using a set of control projects.
\item \textbf{TODO: Criterium.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored. Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

\begin{table}[H]
 \begin{center}
  \caption{Our survey on clone detection tools.} \label{table:dettools}
  \medskip
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
CCFinderSW \cite{semura2017ccfindersw}   &    &             &             & \checkmark            \\ \hline
\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
\end{tabular}
\end{center}
\end{table}

None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool, which is further described in the next chapter.

@@

\subsection{Clone Detection}
To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. On basis of this graph structure, clones are detection. Dependent on the type of clones being detected, transformations may be applied. The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.
